Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-12 qpip0.tex
Add some comments on qpip0 proof

    Protocol:
    \begin{enumerate}
        \item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
        \item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
        \item \label{step:urmila-in-naive}
            The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
            \begin{enumerate}
                \item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
                \item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
                    Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$ \Ethan{Just give it sec. param even though it's just a public coin. Just so it doesn't look strange.} and sends it to the prover.
                \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
                \item
                    If it is a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
                    If it is a Hadamard round, the verifier obtains $v$.
            \end{enumerate}
        \item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
    \end{enumerate}
\end{protocol}

@@

For all $k\leq m$, $d\in \zo^k$, and $\ket{\psi} \in H_{\regX,\regZ}$, define

@@

$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.

Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
    where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities. Note that $z$ is ``sub-normalized", i.e. $\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.

>>>>

    Protocol:
    \begin{enumerate}
        \item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
        \item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
        \item \label{step:urmila-in-naive}
            The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
            \begin{enumerate}
                \item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
                \item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
                    Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
				\item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\xleftarrow{\$}\zo$ and sends it to the prover.
                \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
                \item
                    If it is a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
                    If it is a Hadamard round, the verifier obtains $v$.
            \end{enumerate}
        \item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
    \end{enumerate}
\end{protocol}

@@

For all $k\leq m$, $d\in \zo^k$, \Ethan{and for all $\gamma$?} and $\ket{\psi} \in H_{\regX,\regZ}$, define

@@

$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. Note that we have averaged over $\vec{pk}, \vec{y}$ where as previously everything has fixed $\vec{pk}$ and $\vec{y}$.
\Ethan{Here $\psi$ and $y$ are implicitly dependent on $pk$. Might need to clarify what the expected value over $y$ means.}

Since $\vec{c}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
	where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin \Ethan{typo?} probabilities. Note that $z$ is ``sub-normalized", i.e. $\tr (z) \leq 1 \text{}$, and $\tr(z)$ equals to the probability of getting accepted.
